Analysis and Figures for Gallego et al, 2020

### 2020-09-09 Scripts/Manuscript.Main.Analysis.Rmd
adding modeltesting fit data so user can load it directly rather than rerunning; adding accompanying knitted PDF for supplement.
minor text changes and removing color comments throughout.

#while the changes on the San Juan Island are undetectable (difference in median switch of 0.05, with  p $=$ 0.01).

@@

>>>>

#while the changes on the San Juan Island are negligible (difference in median switch of 0.05, with  p $=$ 0.01).

@@

wilcox.test(x = richness.by.phylum.by.point %>%
                  filter(Year == 2017, Area == "Hood Canal", phylum == "Dinophyceae") %>% 
                    pull(richness),
            y = richness.by.phylum.by.point %>%
                  filter(Year == 2095, Area == "Hood Canal", phylum == "Dinophyceae") %>% 
                    pull(richness))
